Charged pion emission from neutron-rich heavy ion collisions for studies on the symmetry energy

### 2020-08-19 chapters_altFormat/ch_experiment.tex
Second revisions to University

\begin{figure}[!htb]
\includegraphics[width=\textwidth]{fc_overview2.png}
\label{fig:fc_overview2}
\caption{Schematic of the field cage.}
\end{figure}

@@

 \begin{table*}[!htb]
 \centering
\ra{1.1}
\begin{tabular}{@{}ccccccc@{}}\toprule 
\multicolumn{7}{c}{GET electronics settings}\\
\midrule
 Plane & Material & Diameter \si{\micro\metre} & Pitch \si{\milli\metre} & Distance to pad-plane \si{\milli\metre}& Tension \si{\newton} & Voltage \si{\volt}\\ [0.5ex] 
 Anode  & Au-plated W   &  20  &  4  &  4   &  0.5  &  1460  \\
 Ground & BeCu          &  75  &  1  &  8   &  1.2  &  0     \\ 
 Gating & BeCu          &  75  &  1  &  14   &  1.2 &  -110$\pm$ 70\\ 
 \bottomrule
\end{tabular}
\caption{Wire plane properties.}
\label{tb:wireplane}
\end{table*}

@@

\subsection{Gas Properties}
The gas used was a mixture of 90\% Ar and 10\% Methane ($\mathrm{CH_4}$) by volume (P10 gas), and operated just under atmospheric pressure 1 atm. The gas was continually flowed through the field cage and exited into the enclosure volume, finally passing through a bubbler to atmosphere. The gas purity was monitored with an oxygen and water monitor which are the two most concerning contaminants. The water never exceed  100 ppm  and the oxygen level never exceeded 10 ppm, which are the two main contaminants in the gas which can absorb primary electrons \cite{tpcAging}. Figure~\ref{fig:driftvel} shows the drift velocity of P10 gas at 1 atm (\SI{760}{\torr}) as a function of the reduced electric field value given in units of \si{\volt\per\centi\metre\per\torr}. Operating near the peak value of the drift velocity curve minimized the change in the drift velocity as the effective field slightly changes due to slight variations in the pressure. The electric field in the experiment was \SI{125}{\volt\per\centi\per\metre} at \SI{760}{\torr}, giving a reduced electric field \SI{0.17}{\volt\per\centi\metre\per\torr}.

>>>>

\begin{figure}[!htb]
\centering
\includegraphics[width=.8\textwidth]{fc_overview2.png}
\label{fig:fc_overview2}
\caption{Schematic of the field cage.}
\end{figure}

@@

 \begin{table*}[!htb]
 \centering
\ra{1.1}
\begin{tabular}{@{}ccccccc@{}}\toprule 
\multicolumn{7}{c}{GET electronics settings}\\
\midrule
 Plane & Material & Diameter \si{\micro\metre} & Pitch \si{\milli\metre} & $D_{p.p.}$ \si{\milli\metre}& Tension \si{\newton} & Voltage \si{\volt}\\ [0.5ex] 
 Anode  & Au-plated W   &  20  &  4  &  4   &  0.5  &  1460  \\
 Ground & BeCu          &  75  &  1  &  8   &  1.2  &  0     \\ 
 Gating & BeCu          &  75  &  1  &  14   &  1.2 &  -110$\pm$ 70\\ 
 \bottomrule
\end{tabular}
\caption{Wire plane properties. Were $D_{p.p.}$ is the distance from the anode wire to the pad plane.}
\label{tb:wireplane}
\end{table*}

@@

\subsection{Gas Properties}
The gas used was a mixture of 90\% Ar and 10\% Methane ($\mathrm{CH_4}$) by volume (P10 gas), and operated just under atmospheric pressure 1 atm. The gas was continually flowed through the field cage and exited into the enclosure volume, finally passing through a bubbler to atmosphere. The gas purity was monitored with an oxygen and water monitor which are the two most concerning contaminants. The water never exceed  50 ppm  and the oxygen level never exceeded 50 ppm, which are the two main contaminants in the gas which can absorb primary electrons \cite{tpcAging}. Figure~\ref{fig:driftvel} shows the drift velocity of P10 gas at 1 atm (\SI{760}{\torr}) as a function of the reduced electric field value given in units of \si{\volt\per\centi\metre\per\torr}. Operating near the peak value of the drift velocity curve minimized the change in the drift velocity as the effective field slightly changes due to slight variations in the pressure. The electric field in the experiment was \SI{125}{\volt\per\centi\per\metre} at \SI{760}{\torr}, giving a reduced electric field \SI{0.17}{\volt\per\centi\metre\per\torr}.
